---
title: "p8105_hw3_yw3438"
author: "Yuning Wang"
date: "10/3/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(dplyr)
library(ggridges)
library(viridis)
```


## Problem 1

```{r message=FALSE}
# Read the data
library(p8105.datasets)
data("instacart")
```

**To find out the number of aisles and which aisle is the most items ordered from.**
```{r message=FALSE}
aisles_from = instacart %>% 
  group_by(aisle) %>% 
  summarize(n_aisle = n()) %>% 
  arrange(desc(n_aisle))
#Find out how many aisles are there
n_aisles = nrow(aisles_from)
```
It can be concluded that the number of aisles is `r n_aisles` and the most items are ordered from `r pull(aisles_from, aisle)[1]` 

**To draw the plot showing the number of items ordered in each aisle**

```{r  fig.height = 5}
aisle_plot = aisles_from %>% 
  filter(n_aisle > 10000) %>% 
  ggplot(aes(x = n_aisle, y = aisle)) +
  geom_point(aes(color = aisle), alpha = .5) +
  labs(
    title = "Aisle plot",
    x = "Number of items",
    y = "Names of aisles",
    caption = "Data from the instacart") +
  theme(legend.position = "bottom")
  viridis::scale_color_viridis(
    name = "Aisle",
    discrete = TRUE
  )
aisle_plot
```

**To make a table showing the three most popular items in specific aisles**

```{r}
three_pop_table = instacart %>% 
  filter(aisle %in% 
           c("baking ingredients", "dog food care", "packaged vegetables fruits")
         ) %>% 
  group_by(product_name, aisle) %>% 
  summarize(n_product_name = n()) %>% 
  group_by(aisle) %>% 
  filter(min_rank(desc(n_product_name)) < 4) %>% 
  arrange(aisle)
three_pop_table
```


**To make a table about PLA and CIC**

```{r}
pla_cic = instacart %>% 
  filter(product_name %in% c("Pink Lady Apple", "Coffee Ice Cream")) %>% 
  group_by(product_name, order_dow) %>% 
  summarize(
    mean_order_of_day = mean(order_hour_of_day)
  ) %>% 
  mutate(order_dow = recode(order_dow, 
    "0" = "Sunday", "1" = "Monday", "2" = "Tuesday", "3" = "Wednesday",
    "4" = "Thursday", "5" = "Friday", "6" = "Saturday")) %>% 
  pivot_wider(
    names_from = "order_dow",
    values_from = "mean_order_of_day"
  )
pla_cic
```


## Problem 2



